### 2017-12-12 Paper/main.tex

\section{The empirical study}
The empirical study was made using a portfolio built with common stock from the NASDAQ. Such portfolio was composed by 30 common stock randomly sampled from the listed company on NASDAQ. From this portfolio we picked a stock and we tested the hybrid ARIMA versus a naive algorithm who generated buy/selling signals at random. We run the game for 30 matches, and every time we retrained our model with the newer information, leaving aside the older ones.

\subsection{The 30 stocks portfolio}
In order to get the information of the Nasdaq stock we used the API provided by Alphavantage \cite{_alpha_} and we opted for the 1 minute intraday data from which we took the closing price.
\begin{figure}
    \centering
    \includegraphics[width=1\linewidth, ]{Paper/images/Rplot.png}
    \caption{Plot of the closing price of some portfolio's stock}
    \label{portfolo}
\end{figure}

>>>>

\section{The empirical study}
The empirical study was made using a portfolio built with common stocks from the NASDAQ. Such portfolio was composed by 31 common stocks randomly sampled from the listed company on NASDAQ. From this portfolio we picked each stock and we tested the hybrid ARIMA versus a naive algorithm who generated buy/selling signals at random. We run the game for 30 matches, and every time we retrained our model with the newer information, leaving aside the older ones. The time frame was set at 60 intervals.

\subsection{The 30 stocks portfolio}
In order to get the information of the NASDAQ stock we used the API provided by Alphavantage \cite{_alpha_} and we opted for the 1 minute intraday data from which we took the closing price. In \ref{portfolio} a sample of such dataset.

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth, ]{Paper/images/Rplot.png}
    \caption{Plot of the closing price of some portfolio's stock}
    \label{portfolio}
\end{figure}
